---
title: "process_caveman_tbl"
author: "Simon Brunner"
date: "8 June 2017"
output: html_document
---

```{r}
source('../../lib/phylogeny_functions.R')
source('../../lib/LCM_analysis_helper_functions.R')
library(dplyr)
library(tidyr)
library(data.table)
library(data.tree)
library(ape)
library(stringr)
library(RColorBrewer)
```

## Read tree
Tree needs to be in Ape format.
```{r}
tr = readRDS('input/phylo_PD36713b.dat')
```

## Load signature information
The function "load_sig_tables" processes output from HDP into tables with signature exposures, signature colors (in alignment with COSMIC) and plotting order. However, the use of the function is optional. A table of the form hdp_dat$sig_contrib is sufficient to plot a signature tree.
```{r}
path_to_exposures = 'input/exposures.csv'
path_to_decode = 'input/included_sigs.csv'
donor_id = 'PD36713b'
hdp_dat = load_sig_tables(path_to_exposures = path_to_exposures, path_to_decode = path_to_decode, donor_id = donor_id, 
                          max_contrib_thr = 0.1, sig_prefix='sigSBS', prefix_replace = 'sigPCAWG')
```

Here's hdp_dat$sig_contrib - the main table needed for signature tree plotting.
Important features:
* column "donor"
* columns with prefix "sig" that contain signature exposures
* column "cluster_id", which identifies each branch. The IDs listed here need to be contained in the Ape-formatted tree.
* One row per cluster_id/branch.
```{r}
head(hdp_dat$sig_contrib)
```

## Generate a signature tree
```{r}
pdf('output/sig_tree_example.pdf', width=12, height=8)
par(xpd=TRUE, mar=c(12.1, 4.1, 4.1, 2.1))

# First draw a simple tree
draw_nice_tree(tr)

# Then overlay the signature bars
draw_all_edge_sigs(tr, sig_contrib_tbl = hdp_dat$sig_contrib, sig_cols = hdp_dat$sig_colors, sig_order = hdp_dat$sig_order, lwidth=0.4)

# Finally highlight the nodes
highlight_tree_nodes(tr, pch=23, bg='red')

dev.off()
```
The draw_nice_tree function accepts any arguments that are allowed by plot.phylo. For example you can constrain the x-axis to a set number of mutations as follows:
`draw_nice_tree(tr, x.lim=c(0,1000))`